Implications of Measurement Errors in Water Use Estimates for Water Management

### 2024-08-12 Writing/manuscript.tex
manuscript writing started

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{lineno}
% \linenumbers
\usepackage{float}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Implications of Measurement Errors in Water Use Estimates for Water Management},
  pdfauthor={Taro Mieno; Timothy Foster; Nicholas Brozovic; Richael Young},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Implications of Measurement Errors in Water Use Estimates for Water Management}
\author{Taro Mieno\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:tmieno2@unl.edu}{\nolinkurl{tmieno2@unl.edu}}} \and Timothy Foster\footnote{Department of WWW, University of Manchester, \href{mailto:timothy.foster@manchester.ac.uk}{\nolinkurl{timothy.foster@manchester.ac.uk}}} \and Nicholas Brozovic\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:nbrozovic@nebraska.edu}{\nolinkurl{nbrozovic@nebraska.edu}}} \and Richael Young}
\date{}

@@

\section{Main}\label{main}

\subsection{Background}\label{background}

@@

\section{Results}\label{results}

\subsection{Profit under water and proxy quota}\label{profit-under-water-and-proxy-quota}

@@

{\centering \includegraphics[width=432px,]{manuscript_files/figure-latex/profit-quota-water-het-1}

@@

Figure \ref{fig:illust-homegeneous} presents an illustration to build the intuition behind the profit loss due to the use of proxy quota in place of water quota. The red dotted lines indicate the effective water use quota. Under the water quota system, both farmers receive 7 inches of water quota. Since the unconstrained profit maximizing water use is 10.94 inches, both farmers use up all the allocated quota and use 10 inches of water. Under the proxy quota system, they are allocated the same amount of proxy quota. However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively. Both farmers use their allocated amout of water. Under both proxy and water quota systems, the total water use is 14 inches. Farmer B makes 29.8913345 less under the water quota system compared to the proxy quota system. However, Farmer A makes 128.8452417 more under the water quota system compared to the proxy quota system. This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield. As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.

@@

\subsection{The effect of increasing the size of measurement error}\label{the-effect-of-increasing-the-size-of-measurement-error}

@@

{\centering \includegraphics[width=432px,]{manuscript_files/figure-latex/increase-me-degree-1}

@@

\subsection{The effect of allowing trading quota}\label{the-effect-of-allowing-trading-quota}

Allowing quota to be traded among farmers can dramatically change the relative performance of the water- and quota-based regulation.

\begin{itemize}
\tightlist
\item
  Using proxy under the quota system instead of water can hurt welfare severely
\item
  The disadvantage of using proxy almost disappears when trading of quota is allowed
\item
  Proxy trading will never be as profitable as water trading (provide mathematical proof), but the economic loss seems to be very small
\end{itemize}

@@

\subsection{Unfairness}\label{unfairness}

Figure below presents the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue). Ratio of less than 1 indicates making less profit under the quota-based system compared to the water-based system.

\begin{center}\includegraphics{figures/g_profit_ratio} \end{center}

\section{Discussion}\label{discussion}

\section{Methods}\label{methods}

\subsection{}\label{section}

@@

\subsection{Data and Code Availability}\label{data-and-code-availability}

@@

\appendix

\subsection{Distribution of optimal water use under no water use constraints}\label{distribution-of-optimal-water-use-under-no-water-use-constraints}

\begin{center}\includegraphics[width=432px,]{manuscript_files/figure-latex/unnamed-chunk-4-1} \end{center}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{lineno}
% \linenumbers
\usepackage{float}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Implications of Measurement Errors in Water Use Estimates for Water Management},
  pdfauthor={Taro Mieno; Timothy Foster; Nicholas Brozovic},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Implications of Measurement Errors in Water Use Estimates for Water Management}
\author{Taro Mieno\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:tmieno2@unl.edu}{\nolinkurl{tmieno2@unl.edu}}} \and Timothy Foster\footnote{Department of WWW, University of Manchester, \href{mailto:timothy.foster@manchester.ac.uk}{\nolinkurl{timothy.foster@manchester.ac.uk}}} \and Nicholas Brozovic\footnote{Department of Agricultural Economics, University of Nebraska Lincoln, \href{mailto:nbrozovic@nebraska.edu}{\nolinkurl{nbrozovic@nebraska.edu}}}}
\date{}

@@

\hypertarget{main}{%
\section{Main}\label{main}}

\hypertarget{background}{%
\subsection{Background}\label{background}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{profit-under-water-and-proxy-quota}{%
\subsection{Profit under water and proxy quota}\label{profit-under-water-and-proxy-quota}}

@@

{\centering \includegraphics{figures/g_profit_quota_w_vs_p}

@@

Figure \ref{fig:illust-homegeneous} presents an illustration to build the intuition behind the profit loss due to the use of proxy quota in place of water quota. The red dotted lines indicate the effective water use quota. Under the water quota system, both farmers receive 7 inches of water quota. Since the unconstrained profit maximizing water use is 10.94 inches, both farmers use up all the allocated quota and use 10 inches of water. Under the proxy quota system, they are allocated the same amount of proxy quota. However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively. Both farmers use their allocated amout of water. Under both proxy and water quota systems, the total water use is 14 inches. Farmer B makes 30.6035744 less under the water quota system compared to the proxy quota system. However, Farmer A makes 133.2697115 more under the water quota system compared to the proxy quota system. This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield. As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.

@@

\hypertarget{the-effect-of-increasing-the-size-of-measurement-error}{%
\subsection{The effect of increasing the size of measurement error}\label{the-effect-of-increasing-the-size-of-measurement-error}}

@@

{\centering \includegraphics{figures/g_profit_quota_comp_stat}

@@

\hypertarget{the-effect-of-allowing-trading-quota}{%
\subsection{The effect of allowing trading quota}\label{the-effect-of-allowing-trading-quota}}

Allowing quota to be traded among farmers can dramatically change the relative performance of the water- and quota-based regulation. Figure \ref{fig:trading-profit} presents profit for water-based quota, proxy-based quota, water-based quota trading, and proxy-based quota trading regulation systems. As shown in the figure, the disadvantage of using proxy almost disappears when trading of quota is allowed. This is because the inefficiencies in quota allocations are resolved through trading of quota whether it is water or proxy quota. (before trading and after trading?)

@@

Figure \ref{fig:trading-profit-illustration} illustrates

While water-quota and proxy-quota trading perform about the same, water-quota always leads to a higher total profit for a given level of realized water use. In other words, to achieve a certain water use goal, water-quota trading is always to more cost-effective than proxy-quota trading. Under water-quota trading, the margial profit of water is equalized across the farmers, which is a necessary condition to achieve the highest profit for a given level of total water use. Under proxy-quota trading, the marginal profit of proxy is equalized across the farmers, not the margial profit of water (See Appendix \ldots{} for a mathematical proof). However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in Figure \ref{fig:trading-profit}.

\hypertarget{use-of-proxy-can-damage-distributional-equity}{%
\subsection{Use of proxy can damage distributional equity}\label{use-of-proxy-can-damage-distributional-equity}}

Figure \ref{fig:distributional-equity} presents the cumulative probability of the ratio of profit under quota-based relative to water-based system for quota (red) and permit trading (blue). Ratio of less than 1 indicates making less profit under the quota-based system compared to the water-based system. If farmers make just as much profir under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1. For example, under the high degree of measurement error and medium heterogenenity scenario, some farmers would make about the half of what they would make under the water quota system. At the lower end of the distribution are farmers who would be constrained severely by water use quota, but whose water use estiamtes are much higher than their actual water use. At the higher end of the distribution are farmers who would be constrained by water use quota, but whose water use estiamtes are much lower than their actual water use. Famres who suffer significantly under the quota system can develop strong dissatisfaction of the quota-based regulation system, which in turn may lead to installing water meter themselves. If they discover the over-estimation of their water use, they may appeal to legal actions against the administrator for their unfair treatment. Allowind quota trading greatly diminishes the distributional inequality, though not completely. This is because unfortunate farmers who suffered from over-estimation of their water use can now at least purchase proxy quota to increase their production level.

{\centering \includegraphics{figures/g_profit_ratio}

\caption{Distribution of profit under various regulation systems}\label{fig:distributional-equity}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{limitations}{%
\subsection{Limitations}\label{limitations}}

Assumptions.
Temporal

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{section}{%
\subsection{}\label{section}}

@@

\hypertarget{data-and-code-availability}{%
\subsection{Data and Code Availability}\label{data-and-code-availability}}

@@

\hypertarget{appendix-appendix}{%
\appendix}

\hypertarget{distribution-of-optimal-water-use-under-no-water-use-constraints}{%
\subsection{Distribution of optimal water use under no water use constraints}\label{distribution-of-optimal-water-use-under-no-water-use-constraints}}

{\centering \includegraphics{figures/g_opt_w_dist}

\caption{Distribution of optimal water use under no water use constraints}\label{fig:dist-opt-w}
\end{figure}
